---
title: "Homework 4"
type: docs
output:
  blogdown::html_page:
    toc: true
editor_options: 
  chunk_output_type: console
# menu:
#   assignment:
#     parent: Homeworks
#     weight: 4
---



## Tutorial


[Here's what I showed in class](https://www.dropbox.com/s/b5t3tthxjxj32j3/create-new-variable.mov?dl=0).


## Instructions



Answer the questions (below), and keep track of your answers somewhere (a notepad?). You will input your answers into Canvas. **Figure out the answers *BEFORE* opening Canvas**, otherwise you'll run out of time. 



## US Army Enlistment


Let's look at this data which gives us county-level information on military service rates across the USA (variable dictionary below). 

- Download this: <i class="fas fa-download"></i> [Military service data](/files/williams.csv)




```{r, echo=FALSE,message=FALSE,warning=FALSE,results="asis"}
library(tidyverse)
library(pander)
tribble(~Variable, ~Description, 
        "fip", "ID for county",
        "state", "Name of state",
        "county", "Name of county",
        "base", "Is there a military base in this county?\n(1 = yes, 0 = no)",
        "ms_pre_2001", "Average num. of people in county who served in military (pre-2001)", 
        "ms_post_2001", "Average num. of people in county who served in military (post-2001)", 
        "pop2010", "County population",
        "black_2010", "Percent of county who is Black",
        "hispanic_2010", "Percent of county who is Hispanic",
        "hs_grad_2010", "Percent of county with a high school degree",
        "median_household_income_2010", "Median household income in county",
        "unemployment_rate_2010", "Unemployment rate in county",
        "poverty_2010", "Poverty rate in county") %>% 
  pandoc.table()
```



1. Which county had the highest post-2001 military service? 



2. A big problem with (1): that county might have the highest military service because many people enlisted there, **or** it might just be that there's a lot of people who live in that county and that's inflating the military service variable. Create a per-capita enlistment variable called `rate` that divides post-2001 enlistment by county population. Which county has the highest enlistment **rate**?


3. What is the relationship between a county’s unemployment rate and its a military service **rate** (new variable you constructed in question 2)? Plot them together (x-axis = unemployment rate) and add a trend line so you can see the general trend. Roughly, what is that trend? 


4. Look at the military bases variable. How many military bases does the state with the most bases have? 



## iCasualties data


Let's look at this data on virtually all American casualties in the Iraq and Afghanistan wars (variable dictionary below). Each row here is a soldier who died in one of these two wars. 

- Download this: <i class="fas fa-download"></i> [iCasualties data](/files/casualties.csv)


5. Pick a random row/observation — look up the soldier online. What happened to this person? 


6. About what percent of casualties are the result of non-hostile actions (things like accidents, friendly fire, etc.)? Look at the `source` variable. 


7. What was the most common `cause` of death for US soldiers?


8. do anything else with either dataset. Tell me what you did and what you found.


```{r, echo=FALSE,message=FALSE,warning=FALSE,results="asis"}
library(tidyverse)
library(pander)
tribble(~Variable, ~Description, 
        "date", "Date of death",
        "name", "Name of soldier",
        "rank", "Rank of soldier",
        "nationality", "Nationality of soldier",
        "branch", "Branch of military",
        "age", "Age at death",
        "country", "Country (Iraq or Afghanistan)",
        "province", "Province where soldier died",
        "where", "City/locale where soldier died",
        "source", "Source of death (hostile or non-hostile)",
        "cause", "Cause of death",
        "state", "Home state of soldier",
        "city", "Home city/town of soldier",
        "state_pop_2010", "Population in state (2010)") %>% 
  pandoc.table()
```